Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group

### 2019-07-28 tex/Drafts/Draft-1.tex
Abstract edit

  \newcommand\@dotsep{4.5}
  \def\@tocline#1#2#3#4#5#6#7{\relax
    \ifnum #1>\c@tocdepth % then omit
    \else
      \par \addpenalty\@secpenalty\addvspace{#2}%
      \begingroup \hyphenpenalty\@M
      \@ifempty{#4}{%
        \@tempdima\csname r@tocindent\number#1\endcsname\relax
      }{%
        \@tempdima#4\relax
      }%
      \parindent\z@ \leftskip#3\relax \advance\leftskip\@tempdima\relax
      \rightskip\@pnumwidth plus1em \parfillskip-\@pnumwidth
      #5\leavevmode\hskip-\@tempdima{#6}\nobreak
      \leaders\hbox{$\m@th\mkern \@dotsep mu\hbox{.}\mkern \@dotsep mu$}\hfill
      \nobreak
      \hbox to\@pnumwidth{\@tocpagenum{\ifnum#1=1\bfseries\fi#7}}\par% <-- \bfseries for \section page
      \nobreak
      \endgroup
    \fi}

@@

  \title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group}
  \author[Miles Johnson \& Natalie Stewart]{Miles Johnson \& Natalie Stewart\\
    Mentor Oron Propp\\
  Project Suggested by Roman Bezrukavnikov\\ \; \\
  July 31, 2019
  }

   \begin{titlepage}
    \maketitle
    \begin{abstract}
      We consider the Iwahori-Hecke algebra of the symmetric group on $2n + r$ indices with parameter $q \in k^\times$.
      Let $e$ be the smallest integer such that $\brk{e}_q = 0$, or set $e = \infty$ if none exist.
      We modify Khovanov's crossingless matchings to include $2n$ nodes and $r$ anchors, and prove that the corresponding module is isomorphic to the Specht module $S^{(n+r,n)}$ when $e > n + r + 1$.
      Additionally, we prove heuristics in support of the general case.
      Lastly, when $e = 5$, we prove an isomorphism between $D^{(n+r,n)}$ with $r \leq 3$ and some subrepresentations of Jordan-Shor's Fibonacci representation.
    \end{abstract}

>>>>

  \newcommand\@dotsep{4.5}
  \def\@ocline#1#2#3#4#5#6#7{\relax
    \ifnum #1>\c@tocdepth % then omit
    \else
      \par \addpenalty\@secpenalty\addvspace{#2}%
      \begingroup \hyphenpenalty\@M
      \@ifempty{#4}{%
        \@tempdima\csname r@tocindent\number#1\endcsname\relax
      }{%
        \@tempdima#4\relax
      }%
      \parindent\z@ \leftskip#3\relax \advance\leftskip\@tempdima\relax
      \rightskip\@pnumwidth plus1em \parfillskip-\@pnumwidth
      #5\leavevmode\hskip-\@tempdima{#6}\nobreak
      \leaders\hbox{$\m@th\mkern \@dotsep mu\hbox{.}\mkern \@dotsep mu$}\hfill
      \nobreak
      \hbox to\@pnumwidth{\@tocpagenum{\ifnum#1=1\bfseries\fi#7}}\par% <-- \bfseries for \section page
      \nobreak
      \endgroup
    \fi}

@@

  \title[Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras]{Some Graphical Realizations of Two-Row Specht Modules of Iwahori-Hecke Algebras of the Symmetric Group}
  \author[Miles Johnson \& Natalie Stewart]{Miles Johnson \& Natalie Stewart\\
    Mentor : Oron Propp\\
  Project Suggested by : Roman Bezrukavnikov\\ \; \\
  July 31, 2019
  }

   \begin{titlepage}
    \maketitle
    \begin{abstract}
      We consider the Iwahori--Hecke algebra of the symmetric group on $2n + r$ letters with parameter $q$.
      Let $e$ be the smallest positive integer such that the $q$-number $\brk{e}_q = 0$, or set $e = \infty$ if none exist.
      We modify Khovanov's crossingless matchings to include $2n$ ``nodes'' and $r$ ``anchors,'' and prove in the case $e > n + r + 1$ that the associated module is isomorphic to the Specht module $S^{(n+r,n)}$ which corresponds to the partition $(n + r,n) \vdash 2n + r$.
      We then give heuristics in support of the general case, including explicit composition series for $e = n + r + 1$ and for $2n + r \leq 6$. 
      Lastly, when $e = 5$, we prove an isomorphism between the irreducible quotient $D^{(n+r,n)}$ with $r \leq 3$ and some subrepresentations of Jordan--Shor's Fibonacci representation.
      We provide explicit transition matrices between this representation and the crossingless matchings representation for almost all cases where $2n + r \leq 6$.
    \end{abstract}
